---
title: "Evalstock"
author: "Franklin X. Dono"
date: "11/17/2020"
output: ioslides_presentation
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

## Introduction to Evalstock

The app allows you to compare the stock prices of 3 selected stock over a period at a time. The version 1.0 limits you to 10 pre-selected stocks Apple - AAPL, Anglo Gold - AU, Boeing - BA, General Electric - GE, Google - GOOG, Microsoft - MSFT, Newmont _ NEM, Pfizer Inc - PFE, Virgin Galactic Holdings Inc - SPCE, and Walmart Inc - WMT.

## Input requirements

- Three(3) symbols and each symbol selects the ticker of the stock of interest
- Two(2) dates representing the start and end dates of the period of interest
- A click on the Get Stock button to render plot

## Evalstock downloads and prepares stock data

```{r evaldata, echo = TRUE, message=FALSE}
suppressPackageStartupMessages({
library(tidyr)
library(dplyr)
library(ggplot2)
library(quantmod)
})
 symb <- c("AAPL", "MSFT", "NEM")
        mystock <- lapply(symb, function(x) 
                {getSymbols(x,from = "2013-1-1", to = "2020-11-16",
                            periodicity = "daily",auto.assign = FALSE,
                            )})
        names(mystock) <- symb
        adj.prices <- lapply(mystock, Ad)
        adj.prices <- do.call(merge, adj.prices )
        stocks <- as.data.frame(adj.prices) %>%
                gather(index, price)%>% mutate(
                        time = rep(time(adj.prices),length(symb)))

```

## Sample output (Stock price comparison)

```{r evalplot}
g <- ggplot(stocks, aes(time, price, color = index))
        g <- g + geom_line()
        g
```

